Vragenlijst thesis evaluatie

### 2015-06-11 doc/template/chap-9.tex
figuren toegevoegd

\section{Explaining difference between FlipIt with and without virus propagation}
\label{ch2:diffFlip}

@@

Assume that an attacker attacks at time \textit{t}, he doesn't get immediate control over the resource, but he only gains control at time \textit{t + d}, with $d$ denoting the time needed to infect a sufficiently number (or all) nodes. If the defender flips the network before the period $d$ has elapsed (so, somewhere between $t$ and $t + d$), then the attacker will never gain full control over the resource. This implies that the mathematical formulas for gain and benefit need to be adapted to the fact that the attacker loses part of its benefit because of this delay. In the remainder of this paper, we will adapt the formalization of the FlipIt game using the variable $d$. \\

@@

\begin{figure}[hbtp]
\caption{Case 2 where d + deltaA < deltaD}
\centering
\includegraphics[scale=0.5]{../../doc/template/Images/FlipItCase2.png}
\label{fig:case2}
\end{figure}

>>>>

\section{Explaining difference between FlipIt with and without virus propagation}
\label{ch2:diffFlip}
\begin{figure}[hbtp]
\caption{The first game is the basic FlipIt game. The second is a FlipIt game with a delay. During the first flip of the attacker, the defender moves after the delay, causing the attacker to get control over the resource. During the second flip of the attacker, the defender flips at time t+d, causing the defender to take control over the resource before the attacker. During the third and final flip of the attacker, the defender flips during time t+d, causing the attacker to never gain control over the resource. }
\centering
\includegraphics[scale=0.7]{Images/dtFlip.png}
\label{dt}
\end{figure}

@@

Assume that an attacker attacks at time \textit{t}, he doesn't get immediate control over the resource, but he only gains control at time \textit{t + d}, with $d$ denoting the time needed to infect a sufficiently number (or all) nodes. If the defender flips the network before the period $d$ has elapsed (so, somewhere between $t$ and $t + d$), then the attacker will never gain full control over the resource. See figure \ref{dt}. This implies that the mathematical formulas for gain and benefit need to be adapted to the fact that the attacker loses part of its benefit because of this delay. In the remainder of this paper, we will adapt the formalization of the FlipIt game using the variable $d$. \\

@@

\begin{figure}[hbtp]
\caption{All possible cases for the attacker and the defender in Case 2.A where $d + delta_{A} < delta_{D}$. As can be seen, the defender will have control during a period of \textit{d} over the resource when the defender has flipped in the previous interval.}
\centering
\includegraphics[scale=0.7]{../../doc/template/Images/FlipItCase2a.png}
\label{fig:case2}
\end{figure}
